Title

### 2021-05-28 paper/main.tex
Added textcolor

\usepackage[super,sort&compress,comma]{natbib}
\usepackage[left=1.5cm, right=1.5cm, top=1.785cm,
bottom=2.0cm]{geometry}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{{./figures}{../figures}}

@@

Where the near and free states are defined based on the
distance between the graphene layer and the $\alpha-$carbon of the
amino acid projected onto a vector normal to the graphene layer. For a
graphene layer prepared along the XY plane, this is equivalent to the
distance along the Z--axis. This distance will be defined as the
reaction coordinate $\xi$. The cut-off ranges for the near and far
states will be defined based on the PMFs (potentials of mean force)
along $\xi$ of the amino acids, which can be found in the
supplementary materials TODO.

>>>>

\usepackage[super,sort&compress,comma]{natbib}
\usepackage[left=1.5cm, right=1.5cm, top=1.785cm,
bottom=2.0cm]{geometry}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{{./figures}{../figures}}
\usepackage{xcolor}

@@

Where the near and free states are defined based on the
distance between the graphene layer and the $\alpha-$carbon of the
amino acid projected onto a vector normal to the graphene layer. For a
graphene layer prepared along the XY plane, this is equivalent to the
distance along the Z--axis. This distance will be defined as the
reaction coordinate $\xi$. The cut-off ranges for the near and far
states will be defined based on the PMFs (potentials of mean force)
along $\xi$ of the amino acids, which can be found in the
supplementary materials \textcolor{red}{TODO}.
